---
output: html
html-table-processing: none
---

# Code Along in R: Coffee Table

## Start

Setting up.

```{r}
library(gt)
library(tidyverse)
```

Importing the data.

```{r}
coffee_sales <- readr::read_csv("data/coffee-sales.csv")

coffee_sales
```

Let's get the data into gt.

```{r}
gt_tbl_1 <- gt(coffee_sales)

gt_tbl_1
```

## Structure Basics

Add a title to the table to explain contents.

```{r}
gt_tbl_2 <- gt_tbl_1 # |> 

gt_tbl_2
```

Group numerical columns with a spanner. One grouping should be for revenue columns, another should be for profit columns.

```{r}
gt_tbl_3 <- gt_tbl_2 # |> # |>

gt_tbl_3
```

Change Column labels for readability. The column names are:
`icon`, `product`, `revenue_dollars`, `revenue_pct`, `profit_dollars`, and `profit_pct`.

```{r}
gt_tbl_4 <- gt_tbl_3 # |>

gt_tbl_4
```

## Formatting Basics

Format the currency values to make them look better.

```{r}
gt_tbl_5 <- gt_tbl_4 # |>

gt_tbl_5
```

Format the fractional values by turning them into percentages.

```{r}
gt_tbl_6 <- gt_tbl_5 # |>

gt_tbl_6
```

## Styling with tab_style()

Add an 'aliceblue' background to columns pertaining to revenue.

```{r}
gt_tbl_7 <- gt_tbl_6 # |>

gt_tbl_7
```

Add an 'papayawhip' background to columns pertaining to profit.

```{r}
gt_tbl_8 <- gt_tbl_7 # |>

gt_tbl_8
```

Make the text bold in the bottom row (the totals column).

```{r}
gt_tbl_9 <- gt_tbl_8 # |>

gt_tbl_9
```

## Three Last Things

Add a column of bar plots using the monthly revenue column.

```{r}
gt_tbl_10 <- gt_tbl_9 # |>

gt_tbl_10
```

Add images to the `icon` column. The images are in the `img` directory.

```{r}
gt_tbl_11 <- gt_tbl_10 # |>

gt_tbl_11
```

Turn the `NA` cell into a blank cell.

```{r}
gt_tbl_12 <- gt_tbl_11 # |>

gt_tbl_12
```
