---
output: html
html-table-processing: none
---

# Code Along in R: Reactions Table

## Start

Setting up.

```{r}
library(gt)
library(tidyverse)
```

Transforming the data.

```{r}
reactions_mini <-
  reactions |>
  dplyr::filter(cmpd_type == "mercaptan") |>
  dplyr::select(cmpd_name, cmpd_formula, OH_k298, O3_k298, Cl_k298, NO3_k298)

reactions_mini
```

Let's get the data into gt. Plus let's make a stub.

```{r}
gt_tbl_1 <- #

gt_tbl_1
```

## Introducing Units Notation

Add a title to the table to explain contents.

```{r}
gt_tbl_2 <- gt_tbl_1 # |> 

gt_tbl_2
```

Group numerical columns with a spanner. Use this for the label:
`"Reaction Rate Constant (298 K),<br>{{cm^3 molecules^–1 s^–1}}"`

```{r}
gt_tbl_3 <- gt_tbl_2 # |>

gt_tbl_3
```

Change Column labels for readability. The column names are:
`cmpd_formula`, `OH_k298`, `O3_k298`, `NO3_k298`, and `Cl_k298`.

```{r}
gt_tbl_4 <- gt_tbl_3 # |>

gt_tbl_4
```

## Formatting for Science with fmt_chem() and fmt_scientific()

Format the chemical formulas to make them look better.

```{r}
gt_tbl_5 <- gt_tbl_4 # |>

gt_tbl_5
```

Format the numeric values.

```{r}
gt_tbl_6 <- gt_tbl_5 # |>

gt_tbl_6
```

Replace the `NA` values.

```{r}
gt_tbl_7 <- gt_tbl_6 # |>

gt_tbl_7
```

Hide redundant columns.

```{r}
gt_tbl_8 <- gt_tbl_7 # |>

gt_tbl_8
```

## Using the opt_*() Functions for Quick Styling

Use theming to style quickly.

```{r}
gt_tbl_9 <- gt_tbl_8 # |>

gt_tbl_9
```

Don't use the default font.

```{r}
gt_tbl_10 <- gt_tbl_9 # |>

gt_tbl_10
```

Make more space between neighboring values.

```{r}
gt_tbl_11 <- gt_tbl_10 # |>

gt_tbl_11
```
