---
output: html
html-table-processing: none
---

# Code Along in R: Coffee Table

## Start

Setting up.

```{r}
library(gt)
library(tidyverse)
```

Importing the data.

```{r}
coffee_sales <- readr::read_csv("data/coffee-sales.csv")

coffee_sales
```

Let's get the data into gt.

```{r}
gt_tbl_1 <- gt(coffee_sales)

gt_tbl_1
```

## Structure Basics

Add a title to the table to explain contents.

```{r}
gt_tbl_2 <- gt_tbl_1 |> tab_header(title = "Sales of Coffee Equipment")

gt_tbl_2
```

Group numerical columns with a spanner. One grouping should be for revenue columns, another should be for profit columns.

```{r}
gt_tbl_3 <-
    gt_tbl_2 |>
    tab_spanner(label = "Revenue", columns = starts_with("revenue")) |>
    tab_spanner(label = "Profit", columns = starts_with("profit"))

gt_tbl_3
```

Change Column labels for readability. The column names are:
`icon`, `product`, `revenue_dollars`, `revenue_pct`, `profit_dollars`, and `profit_pct`.

```{r}
gt_tbl_4 <-
    gt_tbl_3 |>
    cols_label(
        icon = "",
        product = "Product",
        revenue_dollars = "Amount",
        revenue_pct = "Percent",
        profit_dollars = "Amount",
        profit_pct = "Percent"
    )

gt_tbl_4
```

## Formatting Basics

Format the currency values to make them look better.

```{r}
gt_tbl_5 <- 
    gt_tbl_4 |>
    fmt_currency(
        columns = ends_with("dollars"),
        use_subunits = FALSE
    )

gt_tbl_5
```

Format the fractional values by turning them into percentages.

```{r}
gt_tbl_6 <-
    gt_tbl_5 |>
    fmt_percent(
        columns = ends_with("pct"),
        decimals = 0
    )

gt_tbl_6
```

## Styling with tab_style()

Add an 'aliceblue' background to columns pertaining to revenue.

```{r}
gt_tbl_7 <-
    gt_tbl_6 |>
    tab_style(
        style = cell_fill(color = "aliceblue"),
        locations = cells_body(columns = starts_with("revenue"))
    )

gt_tbl_7
```

Add an 'papayawhip' background to columns pertaining to profit.

```{r}
gt_tbl_8 <-
    gt_tbl_7 |>
    tab_style(
        style = cell_fill(color = "papayawhip"),
        locations = cells_body(columns = starts_with("profit"))
    )

gt_tbl_8
```

Make the text bold in the bottom row (the totals column).

```{r}
gt_tbl_9 <-
    gt_tbl_8 |>
    tab_style(
        style = cell_text(weight = "bold"),
        locations = cells_body(rows = product == "Total")
    )

gt_tbl_9
```

## Three Last Things

Add a column of bar plots using the monthly revenue column.

```{r}
gt_tbl_10 <-
    gt_tbl_9 |>
    cols_nanoplot(
        columns = monthly_sales, 
        plot_type = "bar",
        new_col_name = "nanoplots",
        new_col_label = "Monthly Revenue" 
    )

gt_tbl_10
```

Add images to the `icon` column. The images are in the `img` directory.

```{r}
gt_tbl_11 <-
    gt_tbl_10 |>
    fmt_image(
        columns = icon,
        path = "img/"
    )

gt_tbl_11
```

Turn the `NA` cell into a blank cell.

```{r}
gt_tbl_12 <- gt_tbl_11 |> sub_missing(missing_text = "")

gt_tbl_12
```
